R Coding Exercise

### 2024-06-22 docs/coding-exercise/coding-exerciseElect2016ECruzkml614.qmd
updated exercise 3

# Add regression line
abline(regression, col='darkblue', lwd=1.75)
```
#Additional Data Processing to determine any missing data or NA
#None Found
```{r}
miss_adj_polls=vote_data%>%
  filter(is.na(adjpoll_clinton))
head(miss_adj_polls)
```
#Additional Data Processing to determine any missing data or NA
#None Found 
```{r}
miss_adj_polls=vote_data%>%
  filter(is.na(adjpoll_trump))
head(miss_adj_polls)
```

>>>>

# Add regression line
abline(regression, col='darkblue', lwd=1.75)
```
****************************interpret the clinton and trump raw results************************************************

#Additional Data Processing to determine any missing data or NA
#None Found
```{r}
miss_adj_polls=vote_data%>%
  filter(is.na(adjpoll_clinton))
head(miss_adj_polls)
```
#Additional Data Processing to determine any missing data or NA
#None Found 
```{r}
miss_adj_polls=vote_data%>%
  filter(is.na(adjpoll_trump))
head(miss_adj_polls)
```
